Efficient implementation of penalized regression\\for genetic risk prediction

### 2018-10-01 paper/PRS.tex
last minor changes

\noindent$^{\text{\sf 1}}$Universit\'e Grenoble Alpes, CNRS, Laboratoire TIMC-IMAG, UMR 5525, France, \\
\noindent$^{\text{\sf 2}}$Centre de Bioinformatique, Biostatistique et Biologie Int\'egrative (C3BI), Institut Pasteur, Paris, France.

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-logit}}
\caption{Main comparison of C+T and PLR in scenario \textnumero1 for model ``ADD'' and an heritability of 80\%. Mean of AUC over 100 simulations for PLR and the maximum AUC reported with ``C+T-max''. Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC.}
\label{fig:main-AUC-logit}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-PRS}}
\caption{Comparison of three different p-value thresholds used in the C+T method in scenario \textnumero1 for model ``ADD'' and an heritability of 80\%. Mean of AUC over 100 simulations. Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC.}
\label{fig:main-AUC-PRS}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-ntrain}}
\caption{Comparison of models when varying sample size in scenario \textnumero3 for model ``ADD'' with 300 causal SNPs sampled anywhere on the genome. Mean of AUC over 100 simulations for the maximum values of C+T for three different $r^2$ thresholds ($0.05$, $0.2$ and $0.8$) and PLR as a function of the training size. Upper (lower) panels are presenting results for effets following a Gaussian (Laplace) distribution and left (right) panels are presenting results for an heritability of 0.5 (0.8). Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean of AUC. The blue dotted line represents the maximum achievable AUC.}
\label{fig:main-AUC-ntrain}
\end{figure}

@@

Results of simulations are available at [TODO]. A tutorial on how to start with R packages bigstatsr and bigsnpr is available at \url{https://privefl.github.io/bigsnpr/articles/demo.html}. The two R packages are available on GitHub.

>>>>

\noindent$^{\text{\sf 1}}$Univ.\ Grenoble Alpes, CNRS, Laboratoire TIMC-IMAG, UMR 5525, France, \\
\noindent$^{\text{\sf 2}}$Centre de Bioinformatique, Biostatistique et Biologie Int\'egrative (C3BI), Institut Pasteur, Paris, France.

@@

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-logit}}
\caption{Main comparison of C+T and PLR in scenario \textnumero1 for model ``ADD'' and an heritability of 80\%. Mean AUC over 100 simulations for PLR and the maximum AUC reported with ``C+T-max''. Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean AUC. The blue dotted line represents the maximum achievable AUC.}
\label{fig:main-AUC-logit}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-PRS}}
\caption{Comparison of three different p-value thresholds used in the C+T method in scenario \textnumero1 for model ``ADD'' and an heritability of 80\%. Mean AUC over 100 simulations. Upper (lower) panel is presenting results for effets following a Gaussian (Laplace) distribution. Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean AUC. The blue dotted line represents the maximum achievable AUC.}
\label{fig:main-AUC-PRS}
\end{figure}

\newpage
\begin{figure}[h]
\centerline{\includegraphics[width=\textwidth]{main-AUC-ntrain}}
\caption{Comparison of methods when varying sample size in scenario \textnumero3 for model ``ADD'' with 300 causal SNPs sampled anywhere on the genome. Mean AUC over 100 simulations for the maximum values of C+T for three different $r^2$ thresholds ($0.05$, $0.2$ and $0.8$) and PLR as a function of the training size. Upper (lower) panels are presenting results for effets following a Gaussian (Laplace) distribution and left (right) panels are presenting results for an heritability of 0.5 (0.8). Error bars are representing $\pm 2 \text{SD}$ of $10^5$ non-parametric bootstrap of the mean AUC. The blue dotted line represents the maximum achievable AUC.}
\label{fig:main-AUC-ntrain}
\end{figure}

@@

Results of simulations are available at \url{https://figshare.com/articles/results_zip/7126964}. A tutorial on how to start with R packages bigstatsr and bigsnpr is available at \url{https://privefl.github.io/bigsnpr/articles/demo.html}. The two R packages are available on GitHub.
